Carbon Management Strategies for a Climate-Neutral European Economy

### 2023-12-30 report/submissions/journal/cover_letter/letter.tex
add cover letter

%%%%%%%%%%% Put Recommender(your mentor) Information Here %%%%%%%%%%%
%
\def\name{Philipp Glaum \& Fabian Hofmann
}
%
% List your degree(s), licences, etc. here if you like.
%\def\What{, Your degrees, etc.}
%
% Set the name of your Department or School here
% I honestly don't know why the negative spacing is necessary to get the alignment of the first line correct.  This must be a ``\tikz'' thing.
%%%%%%%%%%%%%%%%%%  School or Department %%%%%%%%%%%%%%%
\def\Where{\hspace{-1.2mm}\textbf{\color{tubred}
	Department of Digital\\Transformation in Energy Systems,\\ TU Berlin
}}

%%%%%%%%%%%%  Additional Contact Information %%%%%%%%%%%
%
% Set your preferred primary contact address here.
\def\Address{Straße des 17. Juni 135
}
%
\def\CityZip{Berlin, 10623 \\
	Germany}
%
% Set your e-mail here
\def\Email{\textbf{\color{tubred}E-mail}: p.glaum@tu-berlin.de}
%
% Set your preferred contact number here
%\def\TEL{\textbf{\color{tubred}Tel/Fax}: +86 28 85412720}
%
% Set your department or personal website here
\def\URL{\textbf{\color{tubred}URL}: {https://www.ensys.tu-berlin.de}}
%

@@

@@

		%%%%%%%%%%% 	Text   %%%%%%%%%%%%%%
		Thank you very much for the opportunity to submit our manuscript to Applied Energy. Hereby we submit the paper “Leveraging the Existing German Transmission Grid with Dynamic Line Rating”.

		In our work, we present the first large-scale investment model that evaluates the benefits of Dynamic Line Rating (DLR) for renewable energy integration.
		Taking Germany as an example, the model includes a high temporal and spatial resolution as well as a high level of detail to enable a realistic representation of the system dynamics.
		The paper appears at an important time as  politicians and Transmission System Operators (TSOs) have recognized the problem of lacking transmission capacities when moving towards high renewable shares in Europe and all over the world.
		% In many official reports DLR is considered as a promising measure to relief the transmission grid.

		Our analysis not only confirms and quantitatively describes transmission system benefits but also shows how the implementation of DLR affects the optimal system design for different shares of renewable power production. By better integrating wind power resources, especially offshore, DLR leads to significant cost savings of 5\% of the system cost, mainly due to the reduced need for cost-driving energy storage. This key finding can be generalized to all countries with normal to high wind resources and is therefore of particular importance for international network operators and the research community. Furthermore, we provide an open-source workflow which can be used to reproduce the results and extend the model to other countries.

		The paper was proofread by Prof. Tom Brown, an energy system expert and native tongue speaker, as well as from Rena Kuwahata from Ampacimon, an expert on transmission lines and DLR applications.

		We want to thank the editor for taking the time to consider the publication of our paper in Applied Energy.

		% What is the novelty of this work? Is the paper appealing to a popular or scientific audience?
		% Why the authors think the paper is important and why the journal should publish it? Has the article
		% been checked by a native tongue speaker with expertise in the field? Are you available as a reviewer
		% for at least three other articles for Applied Energy during the current year? In addition to answering
		% those five questions, the authors should also describe in one or two paragraphs the significance of
		% their work and what new information is described in the manuscript.

>>>>

%%%%%%%%%%% Put Recommender(your mentor) Information Here %%%%%%%%%%%
%
\def\name{Fabian Hofmann, Christoph Tries, Fabian Neumann, Elisabeth Zeyen, Tom Brown.
}
%
% List your degree(s), licences, etc. here if you like.
%\def\What{, Your degrees, etc.}
%
% Set the name of your Department or School here
% I honestly don't know why the negative spacing is necessary to get the alignment of the first line correct.  This must be a ``\tikz'' thing.
%%%%%%%%%%%%%%%%%%  School or Department %%%%%%%%%%%%%%%
\def\Where{\hspace{-1.2mm}\textbf{\color{tubred}
	Department of Digital\\Transformation in Energy Systems,\\ TU Berlin
}}

%%%%%%%%%%%%  Additional Contact Information %%%%%%%%%%%
%
% Set your preferred primary contact address here.
\def\Address{Straße des 17. Juni 135
}
%
\def\CityZip{Berlin, 10623 \\
	Germany}
%
% Set your e-mail here
\def\Email{\textbf{\color{tubred}E-mail}: m.hofmann@tu-berlin.de}
%
% Set your preferred contact number here
%\def\TEL{\textbf{\color{tubred}Tel/Fax}: +86 28 85412720}
%
% Set your department or personal website here
\def\URL{\textbf{\color{tubred}URL}: {https://www.ensys.tu-berlin.de}}
%

@@

\newcommand{\carbon}{CO$_2$}
\newcommand{\hydrogen}{H$_2$}

@@

		%%%%%%%%%%% 	Text   %%%%%%%%%%%%%%
		Thank you for the opportunity to submit our manuscript to Nature Energy. Hereby we submit the paper “\hydrogen{} and \carbon{} Network Strategies for the European Energy System”.

		In our study, we introduce the first large-scale investment model that assesses the co-benefits of a carbon-dioxide and a hydrogen transport system in Europe. The model optimizes the production, transport, and storage of various carriers, including electricity, hydrogen, methane, and carbon-dioxide, across all relevant sectors.

		The paper appears at an important time, with policy makers and industry leaders concretizing plans and investments for hydrogen and carbon-dioxide management systems. In particular, it remains unclear how and to what extent synthetic fuel production and permanent carbon storage (carbon sequestration) should be integrated into the future energy system.

		Our analysis not only confirms the crucial flexibility that \hydrogen{} and \carbon{} transport systems bring to \carbon{} emission neutral energy systems, but also illustrates how their combination further enhances energy efficiency and social welfare. We show that the hydrogen grid optimally transports low-cost hydrogen from areas with good renewable resources to regionally-distributed carbon sources such as industrial clusters and biomass combustion plants to enable synthetic fuel production at site. A carbon-dioxide network, on the other hand, is most cost-beneficial to transport low-cost carbon from point sources near the coast to sequestration sites to permanently store it. In such a setup, the system unlocks most carbon capture potentials from biomass and reduces the reliance on cost-intensive direct air capture. Moreover, the benefits of deploying both networks increase when enforcing a net carbon-removal target, leading to system-cost reductions of 6 billion Euros per year.

		Our analysis underlines the importance of incorporating hydrogen and carbon dioxide networks into European energy policy for a resilient, carbon-neutral or negative future energy system.

		We did not have any prior discussions with a Nature Energy editor about this manuscript. The manuscript has not been published and is not under consideration for publication elsewhere.

		We believe that our findings are in line with the scope of Nature Energy and will be of interest to your readership. We want to thank the editor for taking the time to consider the publication of our paper in Nature Energy.
